\section{Problem Formulation}

\iffalse
\begin{enumerate}
    \item Clearly define the problem or question your research aims to address.
    \item Try to be formal here (use mathematical notation as far as possible)
    \item Clearly state the specific setting you are exploring rather than the overarching problem
\end{enumerate}
\fi

In our investigation, we aim to assess the robustness of contrastive learning frameworks, including notable methodologies such as MoCo, SimCLR, and CMC. To comprehensively evaluate their resilience against data poisoning, we will explore various key aspects identified in the literature. These critical facets encompass strategies such as Data Augmentation, Parallel Augmentation, Architectural choices, Loss Functions, and Data Modalities. For the scope of our study, we will exclusively focus on two widely utilized datasets, namely CIFAR-10 and CIFAR-10C, both of which are image-based. As all of our experiments share the same data modality, the consideration of Data Modality variability becomes unnecessary in this particular context. CIFAR-10 was selected as our baseline dataset, providing a consistent reference point with the same model configuration. This choice allows us to establish a solid foundation for performance assessment, which we can then use to validate the outcomes when applied to the corrupted CIFAR-10C dataset.

Crucial to our research is the pursuit of a deeper understanding of the significance behind the choices made in data augmentation, parallel augmentation, architectural decisions, and loss function selection within the context of contrastive learning. We seek to elucidate why these choices have a bearing on the robustness of these frameworks.

Additionally, we will investigate whether there exists any discernible correlation between the choice of dataset and any of these key aspects. This examination will provide insights into whether certain datasets are more susceptible to the influence of these factors, shedding light on potential dataset-specific nuances that impact the performance of contrastive learning frameworks.

\begin{table}[ht]
    \centering
    \caption{Comparing Models}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Model & Parallel Augmentation & Architecture & Loss Function \\
        \hline
        MoCo V1  & Momentum Encoder & Momentum Contrast & InfoNCE \\
        \hline
        MoCo V2 & Momentum Encoder& Momentum Contrast& InfoNCE\\
        \hline
        SimCLR & Siamese Encoder & End to End & NT-Xent\\
        \hline
        CMC &  & Variance & InfoNCE\\
        \hline
    \end{tabular}
    \label{tab:example}
\end{table}

